Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-21 Thesis/chapter/03-theoretical-background.tex
SEM finished

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Scanning electron Microscopy}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses the \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
%Instead of light, it uses electrons with shorter wavelengths. zum abbilden
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons are \td{created} by either \gls{feg}, where are strong electrical field rips electrons from the bulk and thermionic guns where the filament (tungsten W or \ch{LaB6} (brigther and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
\td{A high \gls{mfp} is needed for electrons to travel from the source to the sample and to the detector. Thus, a very low pressure is in the inside.}
It was used as a preliminary way of checking the surface condition. 
%This allows greater detail. 
why? 
\td{what? how? why?}
what is sputtering, 
how does it work, 
what different kinds of sputtering is there, 
what is is used for? 
\cite{McMullan1995}
\cite{Vernon2000}
\cite{Kaliva2020}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared absorption}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\td{what, how, why?}

\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \m{}) with molecules. \cite{Schwedt2008}
\td{FREE WRITING:}
light is described as periodic electro magnetic wave which moves. 
All \gls{em} waves move with the speed of light c = 300k km /s in vacuum. 
talk about $E=h\cdot v$ and $\nu=c/\lambda$ and $\bar{\nu}=1/\lambda$
shorter wavelength (higher frequencies) carry more energy. 
In practice the spectrum \gls{em} waves are unterteilt in different things. 
from high to low energie: Xray, \gls{uv}, vis, (near, middle and far) \gls{ir}, microwaves and radiowaves. 
Xrays interact with core electrons, \gls{uv} and vis with valence electrons, ir with schwingungne mol rot and translation, microwaves with rotation and radio with electron and nuclear spin. 
molecular vibrations are unterteilt in valenz and deformation vibration.
absorbance pre din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is abhaengig von wave length and molecule structure. 
Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum.

Ein molekule hat $F=3N$ (N anzahl der atome) freiheitsgrade, wobei $F_T=3$ translation und $F_R=3$ (2 für lineare molecules) wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
vibrations are unterteils in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
only vibrations with change in dipole momemnt are \gls{ir} active.

differences to UVVis: transmission instead of absorbance, higher energy left instead right, base line on top instead of bottom.
\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
 In the two strahlen spectrometer the light is split, send through the sample and a reference, combined and send through a monochromator to a detector. 
 In the \gls{ft}\gls{ir} spectrometer the beam is send thourhg the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a bauteil which transforms photons into electircal signals).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Scanning electron Microscopy}
The history of \gls{sem} can be traced back to 1843 when Scottish clockmaker Alexander Bain filed a patent for dissecting an image by scanning. A detailed history of \gls{sem} can be read in a open-to-read paper by McMullan from 1995\cite{McMullan1995}. 
\Gls{sem} is a microscopical technique which allows visualisation of surfaces with features in the nano meter regime. 
While optical microscopes use visible light and optical lenses, \gls{sem} uses accelerated electron beams and electrostatic and electromagnetic lenses.
This allows the generation of much more detailed images due to the shorter wavelengths of electrons compared to light\cite{Kaliva2020}.
The electron beam produces X-rays, elastically backscattered (primary) electrons, inelastic (secondary) electrons and Auger electrons. 
Secondary electrons carry information to conclude morphology and topology of the sample while X-rays can be used to identify the elements. 
Electrons originate from either \gls{feg}, where are strong electrical field rips electrons from the bulk, or from thermionic guns where the filament (tungsten W or \ch{LaB6} (brighter and longer lasting but more expensive)) is heated until electrons are emitted. 
Electrons are then accelerated by a voltage of 2 to 40 kV and bundled into narrow beams\cite{Vernon2000} by lenses.
A high \gls{mfp} is needed for electrons to travel from the source to the sample (and to the detector). 
Thus, a very low pressure is in the inside. 
In this work \gls{sem} was used as a preliminary way of checking the surface condition.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\td{what, how, why?}
\td{QUESTIONS: 
	how does a IR spectr work? monochromator or FT 
	how does FT work 
	how does a beam splitter work? 
	how does detector work? two different for UVVis and MIR
}

\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$\m{} or wave numbers of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy $E$ of a photon, its frequency $\nu$, wavelength $\lambda$ and wave number $\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned in different ranges; 
\td{see figure?}
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
Molecular vibrations can be separated in valence and deformation vibrations.

\td{FREE WRITING:}
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is dependent on wave length and molecule structure. 
%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }

A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translation $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements.

The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
%wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
\td{describe simple IR with monochromator}
\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
 In the two strahlen spectrometer the light is split, send through the sample and a reference, combined and send through a monochromator to a detector. 
 In the \gls{ft}\gls{ir} spectrometer the beam is send thourhg the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a bauteil which transforms photons into electircal signals).
